The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Cache text extracted from pdf
Remove unnecessary comments

```{r}
#| label: extract-pdf-text
#| echo: false
emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

#head_text(emu_theses$text)

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )

```

@@

emu_theses |> 
  find_meta_stopwords(convert_to_regex = FALSE)

emu_theses |> 
  urbanism_stopwords()

>>>>

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache:true

emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )  
```

@@
